---
title: "Monday Warm Up"
author: "Joey"
date: "Monday, 10/18/2021"
output: html_document
---

```{r load-packages, message=FALSE}
library(tidyverse)
library(openintro) 
```
## 1. Problem Solving Code Chunk Labels

Here, we'll be looking at the earthquakes dataset that we used in Lab 4. The first step is to see a glimpse of the data in the knitted markdown file. 

I've provided the code, but what did I do wrong? 

More specifically, what's the fix?

```{r evaluating-data, eval = F}
glimpse(earthquakes)
```

```{r evaluating-data, eval = F}
glimpse(earthquakes)
```

## 2. group_by

```{r earthquakes-per-year, eval = TRUE}
#Missing code, how many earthquakes per year?

  
```

We could also do this using **`count()`**, but that's not what we're asking for here!

## 3. Creating earthquakes2

```{r creating-earthquakes2, eval = FALSE}
#Missing code...


#glimpse() provided  
glimpse(earthquakes2)

```

## 3.2. Creating earthquakes3


```{r creating-earthquakes-3, eval = FALSE}
#Only earthquakes with richter > 7.5, code provided
earthquakes3 <- earthquakes %>% 
  filter(richter > 7.5)

print(earthquakes3)
```


## 4. Joining earthquakes2 and earthquakes3

```{r joining-and-viewing-joins, eval = FALSE}

#Join code is provided
earthquakes_23_left <- earthquakes2 %>%
  left_join(earthquakes3)

earthquakes_23_right <- earthquakes2 %>%
  right_join(earthquakes3)

#Data
head(earthquakes2)
head(earthquakes3)

#Left join
print(earthquakes_23_left)

#Right Join
print(earthquakes_23_right)

```


